A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-10-03 paper.tex
Minor typo

This scheme allows for multiple parameter's fine tunning, granting us the
freedom to experiment with different selection and reproduction strategies
simultaneously, which will impact how fast it finds the solution and the
obtained quality.

>>>>

This scheme allows for multiple parameter's fine tuning, granting us the
freedom to experiment with different selection and reproduction strategies
simultaneously, which will impact how fast it finds the solution and the
obtained quality.
